Kindly Bent to Free Us

### 2019-11-14 kindly/motivation.tex
fixed some grammar

The typing ensures that the mutations do not compromise the state at
the choice point, because they operate on a new state \lstinline/new_g/ created for one
particular branch of the choice.
In particular,
since the \lstinline/set/ function only requires an unrestricted shared borrow,
\lstinline/try_solution/ can captures the borrow \lstinline/&g/
while staying unrestricted.
This also make \lstinline/try_solution/ itself bound to the same
region as \lstinline/&g/. In this example, our region inference
will place the region exactly at the \lstinline/begin//\lstinline/end/
scope.
This allows us to use \lstinline/try_solution/ in
the iteration loop on \cref{line:iter}.
Since \lstinline/&g/ is unrestricted, we could even use a parallel iteration
instead of a sequential one.
As \lstinline/g/ is linear we must free it before returning,
in \cref{line:free:g}, outside of the region.

>>>>

The typing ensures that the mutations do not compromise the state at
the choice point, because they operate on a new state \lstinline/new_g/ created for one
particular branch of the choice.
As the \lstinline/set/ function only requires an unrestricted shared borrow,
the closure \lstinline/try_solution/ remains unrestricted even though
it captures the borrow \lstinline/&g/. 
The price is that \lstinline/try_solution/ cannot escape from
\lstinline/&g/'s region. In this example, inference places the region
around the \lstinline/begin//\lstinline/end/ scope.
Hence, \lstinline/try_solution/ can be used in
the iteration in \cref{line:iter}.
% As \lstinline/&g/ is unrestricted, we could even use a parallel iteration
% instead of a sequential one.
As \lstinline/g/ is linear we must free it outside of the region
before returning (\cref{line:free:g}).
